paper

### 2024-01-23 Toronto_Victims_of_Crimes/outputs/paper/paper.qmd
Update the cross-referencing and labels

### top-level finding, what is the one thing that we learn about the world because of this paper?

@@

The table (@tbl-totalsum_table) below showcases the general trend on the number of victims in different age group. Age information is based on the year that crime was reported. Adult is considered the group at an age of 18 or older. The age of the youth group is between 12 to 17. Below 12 is considered the child group.

@@

# Install the necessary packages if not already installed
# install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "flextable"))

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)
library(flextable)

@@

# Print the table
flextable(head(pivoted_table))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-totalsum-bar
#| tbl-cap: "Number of Reported Victims of Crimes in Different Age Group Over the Years"

@@

Bar graph (@tbl-totalsum-bar) refers table (@tbl-totalsum-table). By visualizing the age group into a bar per year, it is clear to see that majority of victims of reported crimes are adult. Also, the bars are showing ascending order from the year 2014 to 2018 but the reported crimes significantly drop between 2019 and 2020. One possible reason is because of COVID. Correlation between COVID pandemic and report crime rates 논문 찾아서 첨부

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-sv-bar
#| tbl-cap: "Victims Count of Sexual Violation by Age Group Over the Years"

@@

From 2014 to 2020, the trend shows that the adult group is twice the size of the child group. Up until 2020, victims of sexual violation was predominantly adult age group. However, as of 2021, the youth victim group surpass the amount of the adult victim group. 무슨 사건이 일어났을까? 왜 youth group이 더 높아졌는지 사유 찾기

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-a-bar
#| tbl-cap: "Victims Count of Assault by Age Group Over the Years"

@@

# Create a bar graph for Assault with groups for AGE_GROUP
bar_plot <- ggplot(assault_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Victims Count of Assault by Age Group Over the Years",
       x = "Year",
       y = "Number of Reported Victims of Assault",
       fill = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(min(assault_data$REPORT_YEAR), max(assault_data$REPORT_YEAR), by = 1)) +
  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))

@@

The graph (@tbl-a-bar) illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022. COVID does not seem to be a factor that skews the trend. Though, size of both child and youth victim groups got halved. Compared to child victim group, size of youth victim group grows fast.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-r-bar
#| tbl-cap: "Victims Count of Robbery by Age Group Over the Years"

@@

Graph (@tbl-r-bar) depicts that as of 2018, youth group of victims of robbery diminished and it keeps at the lower level. COVID pandemic is the factor of bar graphs on the number of victim of robbery in different age group over the year. In 2020, victims of robbery in every age group significantly decreased. We could assume that lockdown mandate affect the decrease in victims.

@@

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)
library(flextable)

@@

# Pivot the data to have Assault, Sexual Violation, Robbery as columns
pivoted_table2 <- crime_subtype_table %>%
  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)

# Print the table
flextable(head(pivoted_table2))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-crimesubtype-bar
#| tbl-cap: "Victims Count by Crime Subtype Over the Years"

>>>>

### Top-level finding, what is the one thing that we learn about the world because of this paper?

@@

The table (@tbl-totalsum-table) below showcases the general trend on the number of victims in different age group. Age information is based on the year that crime was reported. Adult is considered the group at an age of 18 or older. The age of the youth group is between 12 to 17. Below 12 is considered the child group.

@@

# Install the necessary packages if not already installed
install.packages(c("opendatatoronto", "knitr", "lubridate", "tidyverse", "kableExtra"))

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)
library(kableExtra)

@@

# Print the table with additional styling
kable(pivoted_table, caption = "Count of Child, Youth, and Adult group victims over the years from 2014 to 2022", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Victims Count" = 3))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-totalsum-graph
#| fig-cap: "Number of Reported Victims of Crimes in Different Age Group Over the Years"

@@

Bar graph (@fig-totalsum-graph) refers table (@tbl-totalsum-table). By visualizing the age group into a bar per year, it is clear to see that majority of victims of reported crimes are adult. Also, the bars are showing ascending order from the year 2014 to 2018 but the reported crimes significantly drop between 2019 and 2020. One possible reason is because of COVID. Correlation between COVID pandemic and report crime rates 논문 찾아서 첨부

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-sv-graph
#| fig-cap: "Victims Count of Sexual Violation by Age Group Over the Years"

@@

From 2014 to 2020 (@fig-sv-graph), the trend shows that the adult group is twice the size of the child group. Up until 2020, victims of sexual violation was predominantly adult age group. However, as of 2021, the youth victim group surpass the amount of the adult victim group. 무슨 사건이 일어났을까? 왜 youth group이 더 높아졌는지 사유 찾기

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-a-graph
#| fig-cap: "Victims Count of Assault by Age Group Over the Years"

@@

# Create a bar graph for Assault with groups for AGE_GROUP
bar_plot <- ggplot(assault_data, aes(x = REPORT_YEAR, y = COUNT_, fill = AGE_GROUP)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Year",
       y = "Number of Reported Victims of Assault",
       fill = "Age Group") +
  theme_minimal() +
  scale_x_continuous(breaks = seq(min(assault_data$REPORT_YEAR), max(assault_data$REPORT_YEAR), by = 1)) +
  scale_fill_manual(values = c("Child" = "yellow", "Youth" = "orange", "Adult" = "skyblue"))

@@

The graph (@fig-a-graph) illustrates the ascending trend in number of victims of assault in city of Toronto over the year from 2014 to 2022. COVID does not seem to be a factor that skews the trend. Though, size of both child and youth victim groups got halved. Compared to child victim group, size of youth victim group grows fast.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-r-graph
#| fig-cap: "Victims Count of Robbery by Age Group Over the Years"

@@

Graph (@fig-r-graph) depicts that as of 2018, youth group of victims of robbery diminished and it keeps at the lower level. COVID pandemic is the factor of bar graphs on the number of victim of robbery in different age group over the year. In 2020, victims of robbery in every age group significantly decreased. We could assume that lockdown mandate affect the decrease in victims.

@@

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)
library(kableExtra)

@@

# Pivot the data to have Assault, Sexual Violation, Robbery as columns
pivoted_table <- crime_subtype_table %>%
  pivot_wider(names_from = SUBTYPE, values_from = Victims_Count, values_fill = 0)

# Print the table using kable with additional styling
kable(pivoted_table, caption = "Total number of victims counted for each crime from the year 2014 to 2022", format = "html") %>%
  kable_styling(full_width = FALSE) %>%
  add_header_above(c(" ", "Victims Count" = 3))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-subtype-graph
#| fig-cap: "Victims Count by Crime Subtype Over the Years"
